### 2013-08-30 trunk/papers/2012-sandwich/support.tex
added pair correlation functions
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@1770 40876441-3496-0410-a613-a2fca35b2ae2
Revised support, added Fig. S1 - Davide, Aug 30
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@2143 40876441-3496-0410-a613-a2fca35b2ae2

ISSUE: Temperature?  Temperature: $T = 2.133333 10^{-9}$ CHECK

ISSUE: no redshift?

ISSUE: do we want some free energy numbers?

PENDING

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.35]{s1.jpg}
\end{center}
\caption{As for main manuscript Fig.~1 (initialised to equilibrium blue
phase I), but for the entire simulation
system of 128$^3$ lattice sites. (a) solid volume fraction 1\% and
weak anchoring; (b) 1\% solid volume fraction and strong anchoring;
(c) 5\% solid volume fraction and weak anchoring; (d) 5\% solid
volume fraction and strong anchoring. The view direction in the
main figure is from the left here. There is a reference
particle at the bottom left in each panel which does not take part
in the simulation.}
\end{figure}

\begin{figure}
\includegraphics[scale=0.35]{s2.jpg}
\caption{As for main manuscript Fig.~2 (initialised via a ``quench''
to generate a disordered network), but for the entire simulation
system of 128$^3$ lattice sites. (a) solid volume fraction 1\% and
weak anchoring; (b) 1\% solid volume fraction and strong anchoring;
(c) 5\% solid volume fraction and weak anchoring; (d) 5\% solid
volume fraction and strong anchoring. Again, there is a reference
particle at the bottom left in each case which does not take part
in the simulation.}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.42]{s3.jpg}
\end{center}
\caption{As for main manuscript Fig.~3 (confined geometry with normal
anchoring walls at both top and bottom), but for the entire simulation
system of 256$^2\times$56 lattice sites. Each shows a top view and
side view of the same simulation state. (a) solid volume fraction 1\%
and weak anchoring; (b) 1\% solid volume fraction and strong anchoring;
(c) 4\% solid volume fraction and weak anchoring; (d) 4\% solid
volume fraction and strong anchoring.}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.42]{s4.jpg}
\end{center}
\caption{As for main manuscript Fig.~4 (confined geometry with planar
anchoring walls at both top and bottom), but for the entire simulation
system of 256$^2\times$56 lattice sites. Each shows a top view and
side view of the same simulation state. (a) colloid solid volume fraction 1\%
and weak anchoring; (b) 1\% solid volume fraction and strong anchoring;
(c) 4\% solid volume fraction and weak anchoring; (d) 4\% solid
volume fraction and strong anchoring.}
\end{figure}

@@

{\bf Supporting References}

@@

>>>>

To get from simulation to physical units, we need to calibrate scales of length,
energy and time. For similar mappings, see e.g.~\cite{denniston2}.

The length scale can be set by mapping our half pitch to realistic blue phase
unit cell size, which are in the 100-500 nm range \cite{blue1}. 
For bulk simulations (Fig. 1 and Fig. 3 in the main text), a suitable choice
is that that one simulation unit (lattice site) corresponds to 10 nm. Therefore
the colloidal size in Figs. 1 and 3 corresponds to $\sim$ 50 nm.

To get an energy scale, we choose $A_0 \simeq 10^6$ Pa, which is 
reasonable from Ref.~\cite{blue1} (this is also the choice in
Ref.~\cite{oliver2}). This leads to a simulation unit of
free energy (or stress) equal to $10^{8}$Pa in Figs. 1 and 3.
From the energy and length scales one can map elastic constants to
physical units: for instance the simulation of Fig. 1 corresponds to
a liquid crystal with splay, bend and twist (Frank) elastic constants
equal to 35 pN (or equivalently $K=$70 pN).
\begin{equation}
\frac{a}{b^2} = \frac{27}{2 A_0\gamma} \sim 2-5 \times 10^{-6}
{\rm J}^{-1}\, {\rm m}^{3}.
\end{equation}

For the timescale calibration we use the formula (see e.g.~\cite{denniston})
\begin{equation}
\gamma_1=\frac{2q^2}{\Gamma}\;.
\end{equation}
 which relates the `rotational viscosity' $\gamma_1$, to the ordering strength $q$ and the order parameter mobility $\Gamma$.
In our simulations, we chose $\Gamma = 0.5$, while the value of $\gamma$ used in Fig. 1 leads to $q=1/2$.   
For real liquid crystalline materials, $\gamma_1$ lies usually in range $10^{-2}-1$ Pa s~\cite{deGennes}; we choose for definiteness $\gamma_1 = 1$ Pa s (equivalently 10 poise). Given the previous mapping for free energy (or stress) units, this leads to a simulation unit of time equal to $10^{-8}$ s. The total simulated time in Figs. 1-3 is therefore in the ms range.

To calibrate the electric field strength 
we equate the value of the dimensionless parameter ${\cal E}$ in our 
simulations with that of a hypothetical experiment.
Given the previous value for $A_0$, and a dielectric anisotropy of 10
(or equivalently $\epsilon_a=10\epsilon_0$, with $\epsilon_0$ the
dielectric permittivity of vacuum), we then obtain that an electric field
of 5 V/$\mu$m corresponds to a value of ${\cal E}\sim$0.01.

Given these mappings, all quantities can be easily transformed from
simulation to physical units and vice versa. For example Fig. 1 and 2
use an isotropic viscosity $\eta \simeq$ 0.01 and 0.1 in simulation units,
which translate into $0.01-0.1$ Pa s respectively. This is sensible (if 
slightly low) for a molecular nematogen in the isotropic phase. 
The effective viscosity in ordered phases is higher, but this is ensured
in our model by the coupling to the order parameter.
We note that the density is set to 1 in our simulations: this
corresponds to a fluid density which is about a thousand times larger
than in experiments. This however makes no difference in practice as
the Reynolds number $= \rho V\Lambda/\eta$ (where $V$ is a typical
velocity, in our simulations around $10^{-5}$ in simulation units) 
remains small enough~\cite{codef}.

To summarize the above, our simulations represent BP-forming materials, with the interpretation of the LB units for length, time, and energy density are close to 10 nm, 10 ns, and 100 MPa respectively.

%ISSUE: Temperature?  Temperature: $T = 2.133333 10^{-9}$ CHECK

%ISSUE: no redshift?

%ISSUE: do we want some free energy numbers?

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.8]{SupplFig1.png}
\end{center}
\caption{(A) Schematic representation of the director field
in a cholesteric (left) and within a double twist cylinder (right).
(B) Snapshot of the disclination network in an equilibrated 
blue phase I structure. (C) Same as (B) for an amorphous blue phase III
network.}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.35]{s1.jpg}
\end{center}
\caption{As for main manuscript Fig.~1A-E (initialised to equilibrium blue
phase I), but for the entire simulation system of 128$^3$ lattice sites. (a) 
solid volume fraction 1\% and weak anchoring; 
(b) 1\% solid volume fraction and strong anchoring;
(c) 5\% solid volume fraction and weak anchoring; (d) 5\% solid
volume fraction and strong anchoring. The view direction in the
main figure is from the left here. There is a reference
particle at the bottom left in each panel which does not take part
in the simulation.}
\end{figure}

\begin{figure}
\includegraphics[scale=0.35]{s2.jpg}
\caption{As for main manuscript Fig.~1E-H (initialised via a ``quench''
to generate a disordered network), but for the entire simulation
system of 128$^3$ lattice sites. (a) solid volume fraction 1\% and
weak anchoring; (b) 1\% solid volume fraction and strong anchoring;
(c) 5\% solid volume fraction and weak anchoring; (d) 5\% solid
volume fraction and strong anchoring. Again, there is a reference
particle at the bottom left in each case which does not take part
in the simulation.}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.42]{s3.jpg}
\end{center}
\caption{As for main manuscript Fig.~2A-D (confined geometry with normal
anchoring walls at both top and bottom), but for the entire simulation
system of 256$^2\times$56 lattice sites. Each shows a top view and
side view of the same simulation state. (a) solid volume fraction 1\%
and weak anchoring; (b) 1\% solid volume fraction and strong anchoring;
(c) 4\% solid volume fraction and weak anchoring; (d) 4\% solid
volume fraction and strong anchoring.}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.42]{s4.jpg}
\end{center}
\caption{As for main manuscript Fig.~2E-H (confined geometry with planar
anchoring walls at both top and bottom), but for the entire simulation
system of 256$^2\times$56 lattice sites. Each shows a top view and
side view of the same simulation state. (a) colloid solid volume fraction 1\%
and weak anchoring; (b) 1\% solid volume fraction and strong anchoring;
(c) 4\% solid volume fraction and weak anchoring; (d) 4\% solid
volume fraction and strong anchoring.}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.95\columnwidth]{s5.jpg}
\end{center}
\caption{Pair correlation function for weak ($WR/K=0.23$) and strong ($WR/K=2.3$) anchoring cases considered in the manuscript. (A,B) BPI initialisation with A) volume fraction $\phi=1${\%} and B) $\phi=5${\%}. (C,D) ``quenched system'' with C) $\phi=1${\%} and D) $\phi=5${\%}.}
\end{figure}

@@

{\bf Captions for Supplementary Movies} \\

%{\bf Supporting References}

@@

\bibitem{oliver2}
O. Henrich, K. Stratford, D. Marenduzzo, M. E. Cates, 
\textit{Proc. Acad. Sci. USA} \textbf{107}, 1312 (2010).

\bibitem{codef} M. E. Cates,  et al., 
\textit{J. Phys. Condens. Matter} \textbf{16},  3903 (2004).
